---
title: 'Homework #5'
author: "Brandon Güell & Dani Antos"
date: "11/10/2017"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Load in the data
```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

# Linear Regression

```{r}
m=lm(data= d, log(HomeRange_km2) ~ log(Body_mass_female_mean))
summary(m)
```

## Report: β  coeffiecients (slope and intercept):
```{r}
m$coefficients
```

* **slope: 1.03643**
* **intercept: -9.44123**

# Use bootstrapping to sample from your data 1000 times with replacement:

* lets use the boot package

> make sure to install package "boot"

```{r}
library(boot)

# multiple k

# function to obtain regression weights 
bs <- function(formula, data, indices) {
  d <- data[indices,] # allows boot to select sample 
  fit <- lm(formula, data=d)
  return(coef(fit)) 
} 
# bootstrapping with 1000 replications & replication
results <- boot(data= d, statistic=bs, R=1000, formula=log(HomeRange_km2) ~ log(Body_mass_female_mean))

# view results
results
```

> Just for fun:

```{r}

plot(results, index=1) # intercept 
plot(results, index=2) # log(body mass femaile mean)
```


## Standard Error of Bootstrap:
```{r}
results
```

* **intercept: 0.604880**
* **log(body mass femaile mean): 0.077853**

## Confidence Intervals of Bootstrap:
```{r}
# get 95% confidence intervals for bootstrap
boot.ci(results, type="bca", index=1) # intercept 
boot.ci(results, type="bca", index=2) # log(body mass femaile mean) 
```

* **intercept: -10.707,  -8.371**
* **log(body mass femaile mean): 0.896,  1.198**

## Comparisons of Standard Errors:
```{r}
summary(m)
```
* **intercept: 0.67293**
* **log(body mass femaile mean): 0.08488**

> VS. the Standard Error of Bootstrap:

```{r}
results
```

* **intercept: 0.608714**
* **log(body mass femaile mean): 0.078392**

To us, these seem incredibly similar.


## Comparisons of Confidence Intervals:

```{r}
confint(m, level = 0.95)
```

* **intercept: -10.7720889 -8.110374**
* **log(body mass femaile mean): 0.8685707  1.204292**

> VS. the Confidence Interval of Bootstrap:

```{r}
# get 95% confidence intervals for bootstrap
boot.ci(results, type="bca", index=1) # intercept 
boot.ci(results, type="bca", index=2) # log(body mass femaile mean) 
```

* **intercept: -10.689,  -8.269**
* **log(body mass femaile mean): 0.884,  1.199**

Again, to us, these seem not different.

# Extra Credit

> Write a FUNCTION that takes as its arguments a dataframe, “d”, a linear model, “m” (as a character string, e.g., “logHR~logBM”), a user-defined confidence interval level, “conf.level” (with default = 0.95), and a number of bootstrap replicates, “n” (with default = 1000). Your function should return a dataframe that includes: beta coefficient names; beta coefficients, standard errors, and upper and lower CI limits for the linear model based on your entire dataset; and mean beta coefficient estimates, SEs, and CI limits for those coefficients based on your bootstrap.

```{r}
b.guell.d.antos <- function(d, m, conf.level = 0.95, n = 1000)
{

# model
m = lm(data=d, m)
  
# names
BCoeffNames = names(m$coefficients)

# beta coefficients
data_coeff = coef(summary(m))[, 1]

# data SE and CI
data_SE = coef(summary(m))[, "Std. Error"]
data_CI= confint(m)
data_CI

# Bootstrap stuff:

 library(boot)
  bs <- function(formula, data, indices) {
  d <- data[indices,] # allows boot to select sample 
  fit <- lm(formula, data=d)
  return(coef(fit)) 
  } 
  
# bootstrapping with 1000 replications & replication
results <- boot(data= d, statistic= bs, R=1000, formula= m)

# Bootsrap coefficients
mean_B0= mean(results$t[,1])
mean_B0
mean_B1= mean(results$t[,2])
mean_B1

BootCoeff = c(mean_B0, mean_B1)
BootCoeff


# Bootsrap SE and CI
SE_func <- function(x) {
      sd(x)/sqrt(length(x))
}

BootSE_B0 = SE_func(results$t[,1])
BootSE_B0

BootSE_B1 = SE_func(results$t[,2])
BootSE_B1

BootSE = c(BootSE_B0, BootSE_B1) #must make them into a vector so that it splits in the dataframe nicely..

# confidence intervals
BootB0CI = boot.ci(results, type="bca", index=1) # intercept 
BootB0CI = BootB0CI$bca[,4:5]
BootB0CI

BootB1CI = boot.ci(results, type="bca", index=2) # log(body mass femaile mean) 
BootB1CI = BootB1CI$bca[,4:5]
BootB1CI

# Holy shit... difficult but got it in the right format! yay!
BootCI2.5 = c(BootB0CI[1], BootB1CI[1])
BootCI97.5 = c( BootB0CI[2], BootB1CI[2])
BootCI = cbind(BootCI2.5, BootCI97.5)
BootCI

  spitout <- data.frame( 
     BCoeffNames = BCoeffNames,
		 data_coeff = data_coeff,
     data_SE = data_SE,
		 data_CI = data_CI,
		 
     BootCoeff = BootCoeff,
		 BootSE = BootSE,
		 BootCI) # dont need to name it here because its a dataframe already)
  
  rownames(spitout) <- NULL # get rid of excess row names...

    return(spitout)
  }
```

# Extra Extra Credit

> Graph each beta value from the linear model and its corresponding mean value, lower CI and upper CI from a bootstrap as a function of number of bootstraps from 10 to 200 by 10s. HINT: the beta value from the linear model will be the same for all bootstraps and the mean beta value may not differ that much!

```{r}

```